Tree size, (microhabitat)?, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-08-15 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
issue #39

Community-level tree growth responses to these droughts were modest, with modal resistance values of #, #, and # for 1964-1966, 1977, and 1999, respectively (Fig. 1b). In each drought, roughly 30% of the cored trees suffered growth reductions of 30% or more (resistance <= 0.7): *28.2%* in 1964-66, 31.2% un 1977, and 26.2% in 1999. *Some* trees exhibited increased growth: (resistance > 1.0): #% in 1964-66, #% un 1977, and #% in 1999.

Comparing across droughts, resistance *was highest in 1964-66 drought*, lower in 1999, and lowest in 1977 (Tables 4-5).

  - citing table 3 (the coefficient for individual year) - maybe mention how 77 and 99 have neg coefficients, indicating potential height effect: as time goes on, trees are more affected by drought anyways because they grow taller

>>>>

Community-level tree growth responses to these droughts were modest, with modal resistance values of #, #, and # for 1964-1966, 1977, and 1999, respectively (Fig. 1b). In each drought, roughly 30% of the cored trees suffered growth reductions of 30% or more (resistance <= 0.7): *28.2%* in 1964-66, 31.2% un 1977, and 26.2% in 1999. *Some* trees exhibited increased growth: (resistance > 1.0): #% in 1964-66, #% un 1977, and #% in 1999. Within the context of mixed effects models, there were signficiant differences among droughts (Table 4), and drought year came out as a factor in all top models (Table 5). In all cases, resistance *was highest in 1964-66 drought*, lower in 1999, and lowest in 1977 (Tables 4-5).
